---
title: "Graphing p4:"
date: "Date: `r Sys.Date()`"
output: 
# radix::radix_article: # radix is a newer alternative that has some advantages over `html_document`.
  html_document: 
    keep_md: no
    toc: yes
    toc_float: 
      collapsed: true
      smooth_scroll: true
    highlight: tango
    theme: spacelab
---

# overview

This document narrates the demonstration of the `(prep + plot + print) + place` technique using the data from ... .

We will proceed in the following sequence of phases:

- PHASE 0 - explore the data
- PHASE 1 - build the plot
- PHASE 2 - build the `plot` function
- PHASE 3 - isolate the `prep` step
- PHASE 4 - isolate the `print` step
- PHASE 5 - serialize graph production
- PHASE 6 - how to `place` graphs onto the canvas


<!--  Set the working directory to the repository's base directory; this assumes the report is nested inside of two directories.-->
```{r, echo=F, message=F} 
# cat("Working directory: ", getwd())
library(knitr)
opts_knit$set(root.dir='../../')  #Don't combine this call with any other chunk -especially one that uses file paths.
```

<!-- Set the report-wide options, and point to the external code file. -->
```{r set-options, echo=F}
# cat("Working directory: ", getwd())
report_render_start_time <- Sys.time()
opts_chunk$set(
  results      = 'show', 
  comment      = NA, 
  tidy         = FALSE,
  # dpi        = 400,
  # out.width  = "650px", #This affects only the markdown, not the underlying png file.  The height will be scaled appropriately.
  fig.width    = 7, 
  fig.height   = 4, 
  fig.path     = 'figure-png/'
)

echo_chunks    <- TRUE #Toggle for debugging.
message_chunks <- FALSE #Toggle for debugging.
options(width=100) #So the output is 25% wider than the default.
read_chunk("./analysis/.../rfile.R") #This allows knitr to call chunks tagged in the underlying *.R file.
```
# set the scene

## load packages
<!-- Load packages, or at least verify they're available on the local machine.  Suppress the output when loading packages. --> 
```{r load-packages, echo=echo_chunks, message=message_chunks}
```
## load sources
<!-- Load 'sourced' R files.  Suppress the output when loading sources. --> 
```{r load-sources, echo=echo_chunks, message=message_chunks}
```
## declare globals
<!-- Load any global functions and variables declared in the R file.  Suppress the output. --> 
```{r declare-globals, echo=echo_chunks, results='show', message=message_chunks}
```

<!-- Declare any global functions specific to a Rmd output.  Suppress the output. -->
```{r rmd-specific, echo=echo_chunks, message=message_chunks}
# Put presentation-specific code in here.  It doesn't call a chunk in the codebehind file.
#   It should be rare (and used cautiously), but sometimes it makes sense to include code in Rmd 
#   that doesn't live in the codebehind R file.
```
## load data
<!-- Load the datasets.   -->
```{r load-data, echo=echo_chunks, results='show', message=message_chunks}
```

# PHASE 0 - explore 

## tweak data
<!-- Tweak the datasets.   -->
```{r tweak-data, echo=echo_chunks, results='show', message=message_chunks}
```
## inspect-1 raw
```{r inspect-data-1, echo=echo_chunks, results='show', message=message_chunks}
```
## declare components
```{r declare-components, echo=echo_chunks, results='show', message=message_chunks}
```
## inspect-2 categorical
```{r inspect-data-2, echo=echo_chunks, results='asis', message=FALSE}
```

## inspect-3 continuous
```{r inspect-data-3, echo=echo_chunks, results='asis', message=message_chunks}
```

# PHASE 1 - graph

## sketch the space
```{r phase-1-graph, echo=echo_chunks, results='show', message=message_chunks}
```

## graph-1 basic
```{r phase-1-graph-1, echo=echo_chunks, results='show', message=message_chunks,out.width="960px"}
```

# PHASE 2 - make plot

```{r phase-2-make_plot, echo=echo_chunks, results='show', message=message_chunks,fig.width=11, fig.height=7,out.width="960px"}
```

```{r phase-2-make_plot-1, echo=echo_chunks, results='show', message=message_chunks,fig.width=11, fig.height=17,out.width="960px"}
```

# PHASE 3 - prep data

```{r  phase-3-prep_data-1, echo=echo_chunks, results='show', message=message_chunks,out.width="960px"}
```

# PHASE 4 - print plot

```{r phase-4-print_plot, echo=echo_chunks, results='show', message=message_chunks,out.width="960px"}
```

```{r phase-4-print_plot-1, echo=echo_chunks, results='show', message=message_chunks,out.width="960px"}
```

# PHASE 5 - serialize

```{r phase-5-serialize, echo=echo_chunks, results='show', message=message_chunks,out.width="960px"}
```

# PHASE 6 - place plot

```{r phase-6-place_plot, echo=echo_chunks, results='show', message=message_chunks,out.width="960px"}

```

# concluding remarks

Please note that this is not a "method" or a "framework", but merely an example of how to organize a particular comparison. 

# future direction


session information
===========================================================================

For the sake of documentation and reproducibility, the current report was rendered in the following environment.  Click the line below to expand.

<details>
  <summary>Environment <span class="glyphicon glyphicon-plus-sign"></span></summary>
```{r session-info, echo=FALSE}
if( requireNamespace("devtools", quietly = TRUE) ) {
  devtools::session_info()
} else {
  sessionInfo()
} 
```
</details>

```{r session-duration, echo=FALSE}
report_render_duration_in_seconds <- round(as.numeric(difftime(Sys.time(), report_render_start_time, units="secs")))
```

Report rendered by `r Sys.info()["user"]` at `r strftime(Sys.time(), "%Y-%m-%d, %H:%M %z")` in `r report_render_duration_in_seconds` seconds.
