---
title: "DSS - Power Tips November 2020"
author: "Andriy Koval"
date: "11/29/2020"
output: html_document
---
  
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, message=FALSE}
library(magrittr)
library(dplyr)
library(ggplot2)
library(rlang)
```


# 1  


```{r}
mtcars %>% 
  filter(cyl == 4) %>%
    ggplot(aes(x = mpg, y = disp ))+
      geom_point()+
      geom_point(shape = 0, size = 4,data = mtcars %>% filter(cyl==4, gear == 4))

# Re-write with auto-reference
mtcars %>% 
  filter(cyl == 4) %>%
  {
    ggplot(.,aes(x = mpg, y = disp ))+
      geom_point()+
      geom_point(shape = 0, size = 4,data = . %>% filter(gear == 4))
  }


```



# References

- [How to make your own ggplo2 functions](https://www.youtube.com/watch?v=9v9-EpTuwk0)
- [Tidy Eval Meets ggplot2](https://www.onceupondata.com/2018/07/06/ggplot-tidyeval/)
- [Tidy evaluation, most common actions](https://edwinth.github.io/blog/dplyr-recipes/)

# 1. Placing scales on all facets

When faceting a plot, we may need to place axis labels on each facet (especially if we have many of them):
```{r}
mtcars %>% 
  ggplot(aes(x=disp, y = mpg))+
  geom_point()+
  facet_wrap(~cyl, ncol=1)+ 
  theme_dark()
```

One way of achieving this is to use `scale = "free_x"` argument, but if data on the faceted levels covers different ranges of values, the limits of the scale will be adjusted:
```{r}
mtcars %>% 
  ggplot(aes(x=disp, y = mpg))+
  geom_point()+
  # facet_wrap(~cyl, ncol=1) 
  facet_wrap(~cyl, ncol=1, scales = "free_x")+ # puts tickmarks, but distorts scale
  theme_dark()
```

Comes in the `lemon` package, which provides functions `racet_rep_wrap()` and `facet_rep_grid()` to offer exactly this flexibility. You can also use the arguments you  normally pass to `facet_wrap()` or `facet_grid()` respectively:
```{r}
mtcars %>% 
  ggplot(aes(x=disp, y = mpg))+
  geom_point()+
  # facet_wrap(~cyl, ncol=1) 
  # facet_wrap(~cyl, ncol=1, scales = "free_x") # puts tickmarks, but distorts scale
  lemon::facet_rep_wrap(~cyl,ncol=1, repeat.tick.labels = TRUE)+
  theme_dark()
```

# 2. Tidy Evals with {{

When turning your ggplots into functions, we can use `aes_string` funtion to pass quoted strings as variable names

```{r}
make_faceted_scatter <- function(d,xvar,yvar){
  mtcars %>% 
    ggplot(aes_string(x=xvar, y = yvar))+
    geom_point()+
    theme_dark()
}
mtcars %>% make_faceted_scatter("disp","mpg")
```

However, passing an unquoted variable names to function required resorting to `rlang` package to translate bares (unquoted names) to quosures in functions:
  
```{r include=FALSE}
make_faceted_scatter <- function(d,xvar,yvar){
  xvar_enquo <- rlang::enquo(xvar)
  yvar_enquo <- rlang::enquo(yvar)
  mtcars %>% 
    ggplot(aes(x=!!xvar_enquo, y = !!yvar_enquo))+
    geom_point()+
    theme_dark()
}
mtcars %>% make_faceted_scatter(disp,mpg)
```

Unfortunately, this did not play well with facets. However, since  `0.4.0` version, `rlang` provides a shortcut for this implementation using `{{}}`, which pairs up with the new (`ggplot2 3.0.0`) helper function `vars()` in `facet_wrap()` to make it work: 
  
```{r}
library(rlang)
make_faceted_scatter <- function(d,xvar, yvar,fvar){
  mtcars %>% 
    ggplot(aes(x={{xvar}}, y = {{yvar}}))+
    geom_point()+
    lemon::facet_rep_wrap(vars({{fvar}}),ncol=1, repeat.tick.labels = TRUE)+
    theme_dark()
}
mtcars %>% make_faceted_scatter(disp,mpg,cyl)
```

